### 2020-06-23 text/article_vedrovice.Rmd
separate figure labels from code block titles

```{r spat-funs, fig.cap = "Functions *G*, *F*, *K* and *T*. *Dashed line* -- theoretical curve under CSR, *solid line* -- empirical curve, *gray area* -- envelope."}
knitr::include_graphics(here("plots", "pointprocess_fun.pdf"))
```

```{r neigh-sex, fig.cap = "Mean neighbors in a given sex category. *Gray area* -- density estimation for the simulated data, *vertical line* -- observed value."}
knitr::include_graphics(here("plots", "prob_neighbour_sex.pdf"))
```

>>>>

```{r label-spat-funs}
label_spat_funs <- paste("Functions *G*, *F*, *K* and *T*.",
"*Dashed line* -- theoretical curve under complete spatial randomness, *solid line* -- empirical curve, *gray area* -- envelope.")
```
```{r spat-funs, fig.cap = label_spat_funs}
knitr::include_graphics(here("plots", "pointprocess_fun.pdf"))
```

```{r label-neigh_sex}
label_neigh_sex <- paste("Mean neighbors in a given sex category",
"*Gray area* -- density estimation for the simulated data, *vertical line* -- observed value.",
"*F* -- female, *M* -- male, *n. a.* -- non adult.")
```
```{r neigh-sex, fig.cap = label_neigh_sex}
knitr::include_graphics(here("plots", "prob_neighbour_sex.pdf"))
```
